---
title: "rfvip Vignette"
author: "Kelvyn Bladen"
date: "`r Sys.Date()`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{rfvip Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

distdiffR is an R package for bivariate two-sample tests of distributional equality.
The package provides a collection of nonparametric permutation tests for distributional equality. The tests
make use of statistics between empirical cumulative distribution functions averaged across a series of rotations
and / or toroidal shifts of the pooled samples. The variety of tests with their respective parameters can be
called from the main function distdiffr(). It takes as input two bivariate samples (not necessarily the
same size) in the form of two-column matrices.

## Examples

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```
